---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/"
)
```

The Benford Analysis Grouped (`benford.analysis.grouped`) is a modification of the benford.analysis package by carloscinelli. This version allows for Benford tests to be run by group, with intelligent selection of digits to be tested, and selective reporting of significant and / or most anomalous results.

## How to install the package from GitHub

To install the GitHub version you need to have the package `devtools` installed. Make sure to set the option `build_vignettes = TRUE` to compile the package vignette. 

```{r, eval = FALSE}
# install.packages("devtools") # run this to install the devtools package
devtools::install_github("th-chau/benford.analysis.grouped", build_vignettes = TRUE)
```

## Example usage

Please see documentation of benford.analysis for details.

Documentation outlining new commands in this package will be uploaded soon.